\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-01-23 papers/jss/article.Rnw
Add a few improvements to the abstract suggested by Arif Merchant to make it more self contained.  After the first sentence explains that pipelines of applications need to communicate with each other, briefly describe the problem with common solutions such as CSV files in a new sentence, before transitioning to the third sentence to talk about protocol buffers.  Then after this, uncomment Jeroen's sentence from elsewhere in the paper which I had moved here which describes how they offer a unique combination of ...
After this change, section 2 starts at the top of page 3 instead of
the last lin

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
% Spelling Standardization:
% Protocol Buffers, not protocol buffers
% large-scale, not large scale

@@

%% an abstract and keywords
\Abstract{
Modern data collection and analysis pipelines often involve
a sophisticated mix of applications written in general purpose and
specialized programming languages.  Protocol Buffers are a popular
method of serializing structured data between applications---while remaining
independent of programming languages or operating system.  The
\CRANpkg{RProtoBuf} package provides a complete interface between this
library and the \proglang{R} environment for statistical computing.
%TODO(ms) keep it less than 150 words.
% Maybe add Jeroen's sentence:
% JO: added this sentence to the conclustion, but could use it in abstract as well.
% They offer a unique combination of features, performance, and maturity that seems
% particulary well suited for data-driven applications and numerical
% computing.
}
\Keywords{\proglang{R}, \pkg{Rcpp}, protocol buffers, serialization, cross-platform}
\Plainkeywords{R, Rcpp, protocol buffers, serialization, cross-platform} %% without formatting
%% at least one keyword must be supplied

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Spelling Standardization:
% Protocol Buffers, not protocol buffers
% large-scale, not large scale
% Oxford comma: foo, bar, and baz.

@@

%% an abstract and keywords
\Abstract{
Modern data collection and analysis pipelines often involve
a sophisticated mix of applications written in general purpose and
specialized programming languages.  
There are many formats used to import and export data between
different programs or systems, such as CSV, but they are usually
verbose, inefficient, not type-safe, or tied to a specific programming language.
Protocol Buffers are a popular
method of serializing structured data between applications---while remaining
independent of programming languages or operating system.
They offer a unique combination of features, performance, and maturity that seems
particulary well suited for data-driven applications and numerical
computing.
The
\CRANpkg{RProtoBuf} package provides a complete interface to Protocol
Buffers from the
\proglang{R} environment for statistical computing.
%TODO(ms) keep it less than 150 words.
% Maybe add Jeroen's sentence:
% JO: added this sentence to the conclustion, but could use it in abstract as well.
% They offer a unique combination of features, performance, and maturity that seems
% particulary well suited for data-driven applications and numerical
% computing.
}
\Keywords{\proglang{R}, \pkg{Rcpp}, protocol buffers, serialization, cross-platform}
\Plainkeywords{R, Rcpp, protocol buffers, serialization, cross-platform} %% without formatting
%% at least one keyword must be supplied
